Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-01-15 lqg-strings.tex
Moved bimetric section to appendix, recovered my section on lqg strings, some compilation errors remaining

\begin{equation}\label{eqn:polyakov-flat}
	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
\end{equation}
Here $\mu, \nu \in \{0,1,\ldots,D-1\}$ are co-ordinates of the $D$ dimensional worldvolume (the geometry in which the string propagates), $a,b \in \{0,1\}$ are co-ordinates on the string worldsheet, $X^\mu$ are the embedding co-ordinates which specify the location of a point on the string worldsheet in the bulk worldvolume, $\eta_{\mu\nu}$ is the flat Minkowski metric on the worldvolume, $g_{ab}$ is the metric on the string worldsheet, $T$ is the string tension and $\tau, \sigma $ are the co-ordinates on the string worldsheet.

@@

Following the procedure done in $\cite{Zwiebach2009A-First}$, the correction(\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
\begin{equation} \label{eqn:modified-NG-eom}
	\mathrm{EoM:} \partial _{\tau} \PS ^{\tau} _{\mu} + \partial _{\sigma} \PS ^{\sigma} _{\mu} = 0
\end{equation}
and
\begin{equation} \label{eqn:modified-NG-bc}
	\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} \big| _{\sigma = 0} ^{\sigma = \sigma _1} = 0 ,
\end{equation}
where
\begin{align} \label{eqn:modified-NG-tau-currents}
	\PS ^{\tau} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial \Dot{X}^{\mu}} \nonumber                                                                 \\
	                   & = - T \frac{(\Dot{X} \cdot X') X' _{\mu} - (X')^2 \Dot{X}_{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
	                   & = \PS ^{\tau} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
\end{align}
\begin{align} \label{eqn:modified-NG-sigma-currents}
	\PS ^{\sigma} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial X^{\prime \mu}} \nonumber                                                                     \\
	                     & = - T \frac{(\Dot{X} \cdot X') \Dot{X}_{\mu} - (\Dot{X})^2 X' _{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
	                     & = \PS ^{\sigma} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
\end{align}
and $\PS ^{\tau} _{\mu (N G)}$, $\PS ^{\sigma} _{\mu (N G)}$ are the regular Nambu-Goto world-sheet currents.

@@

@@

\hline

>>>>

\begin{equation}
	S_{P} = -\frac{T}{2} \int \diff \tau \wedge \diff \sigma \sqrt{-g} g^{ab} \partial_a X^\mu \partial_b X^\nu \eta_{\mu\nu}.
\end{equation}
Here $\mu, \nu \in \{0,1,\ldots,D-1\}$ are co-ordinates of the $D$ dimensional worldvolume (the geometry in which the string propagates), $a,b \in \{0,1\}$ are co-ordinates on the string worldsheet, $X^\mu$ are the embedding co-ordinates which specify the location of a point on the string worldsheet in the bulk worldvolume, $\eta_{\mu\nu}$ is the flat Minkowski metric on the worldvolume, $g_{ab}$ is the metric on the string worldsheet, $T$ is the string tension and $\tau, \sigma $ are the co-ordinates on the string worldsheet.

@@

Following the procedure done in \cite{Zwiebach2009A-First}, the correction(\ref{eqn:modified-NG-action}) does not change the form of the equations of motion and neither of the boundary conditions, i.e they are still given by
\begin{equation} \label{eqn:modified-NG-eom}
	\mathrm{EoM:} \partial _{\tau} \PS ^{\tau} _{\mu} + \partial _{\sigma} \PS ^{\sigma} _{\mu} = 0
\end{equation}
and
\begin{equation} \label{eqn:modified-NG-bc}
	\mathrm{B.C.:} \PS ^{\sigma} _{\mu} \delta X^{\mu} \big| _{\sigma = 0} ^{\sigma = \sigma _1} = 0 ,
\end{equation}
where
\begin{align} \label{eqn:modified-NG-tau-currents}
	\PS ^{\tau} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial \Dot{X}^{\mu}} \nonumber                                                                 \\
	                   & = - T \frac{(\Dot{X} \cdot X') X' _{\mu} - (X')^2 \Dot{X}_{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
	                   & = \PS ^{\tau} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
\end{align}
\begin{align} \label{eqn:modified-NG-sigma-currents}
	\PS ^{\sigma} _{\mu} & = \frac{\partial \Lagr ' _{N G}}{\partial X^{\prime \mu}} \nonumber                                                                     \\
	                     & = - T \frac{(\Dot{X} \cdot X') \Dot{X}_{\mu} - (\Dot{X})^2 X' _{\mu}}{\sqrt{- h}} \left( 1 + \frac{g \Delta}{2 (- h)} \right) \nonumber \\
	                     & = \PS ^{\sigma} _{\mu (N G)} \left( 1 + \frac{g \Delta}{2 (- h)} \right)
\end{align}
and $\PS ^{\tau} _{\mu (N G)}$, $\PS ^{\sigma} _{\mu (N G)}$ are the regular Nambu-Goto world-sheet currents.

@@

\section{The Quantum Klein-Gordon String} \label{sec:quantum-KG-string}

In the following, we proceed to quantize the Klein-Gordon string via canonical covariant quantization, in a manner much similar to those found in \cite{Tong2009Lectures} and \cite{Green2012Superstring}. To start, we calculate the momentum canonical to the embbeding fields $X^{\mu}$, which reads
\begin{multline} \label{eqn:canonical-momentum}
	\Pi _{\mu} (\tau , \sigma) = F^{-} \frac{i}{(4 \pi \alpha ')^2} \sum _{p} \big( - \alpha ^{\nu} _{p} \e ^{i (- E_{p} \tau + p \sigma)} + \\
	+ (\alpha ^{\nu} _{- p})^{*} \e ^{i (E_{p} \tau + p \sigma)} \big) \eta _{\nu \mu} ,
\end{multline}
and then we proceed to turn the equal-time Poisson bracket relations
\begin{equation} \label{eqn:Poisson-brackets-1}
	\left\{ X^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\} = \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
\begin{equation} \label{eqn:Poisson-brackets-2}
	\left\{ X^{\mu} (\tau , \sigma) , X^{\nu} (\tau , \sigma ') \right\} = 0 = \left\{ \Pi ^{\mu} (\tau , \sigma) , \Pi ^{\nu} (\tau , \sigma ') \right\}
\end{equation}
into equal-time commutation relations between the now operators $\Hat{X}^{\mu}$ and $\Hat{\Pi}^{\nu}$:
\begin{equation} \label{eqn:canonical-commutator-1}
	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] \equiv i \delta (\sigma - \sigma ') \eta ^{\mu \nu}
\end{equation}
\begin{equation} \label{eqn:canonical-commutator-2}
	\Big[ \Hat{X}^{\mu} (\tau , \sigma) , \Hat{X}^{\nu} (\tau , \sigma ') \Big] = 0 = \Big[ \Hat{\Pi}^{\mu} (\tau , \sigma) , \Hat{\Pi}^{\nu} (\tau , \sigma ') \Big] .
\end{equation}
From these relations, we get commutation relations for the vibrational modes $\Hat{\alpha}^{\mu} _{p}$ and $(\Hat{\alpha}^{\nu} _{- k})^{\dagger}$:
\begin{equation} \label{eqn:non-vanishing-commutator}
	\Big[ \Hat{\alpha}^{\mu} _{p} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p , - k}
\end{equation}
\begin{equation} \label{eqn:vanishing-commutators}
	\Big[ \Hat{\alpha}^{\mu} _{p} , \Hat{\alpha}^{\nu} _{k} \Big] = 0 = \Big[ (\Hat{\alpha}^{\mu} _{- p})^{\dagger} , (\Hat{\alpha}^{\nu} _{- k})^{\dagger} \Big] ,
\end{equation}
which are just harmonic oscillator relations with
\begin{align}
	\Hat{a}^{\mu} _{p}             & = \Hat{\alpha}^{\mu} _{p} \label{eqn:annihilation-operator}                                       \\
	(\Hat{a}^{\mu} _{p})^{\dagger} & = (\Hat{\alpha}^{\mu} _{p})^{\dagger} , \ \mathrm{for} \ p \neq 0 . \label{eqn:creation-operator}
\end{align}
For $p = 0$ we have the center of mass momentum operator $\Hat{p}^{\mu}$. As usual, we define a vacuum state for the string to obey
\begin{equation} \label{eqn:annihilation-vacuum}
	\Hat{a}^{\mu} _{p} \ket{0} = 0 , \ \mathrm{for} \ p \neq 0 ,
\end{equation}
and for $p = 0$
\begin{equation} \label{eqn:momentum-vacuum}
	\Hat{p}^{\mu} \ket{0} = p^{\mu} \ket{0} .
\end{equation}
Our Fock space is built from the vacuum state $\ket{0}$ by operating with a sequence of creation operators
\begin{multline} \label{eqn:general-state}
	\ket{\psi} = ((a^{\mu _{1}} _{1})^{\dagger})^{n_{\mu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\mu _2}} ... \times \\
	\times ((a^{\nu _1} _{1})^{\dagger})^{n_{\nu _1}} ((a^{\mu _2} _{2})^{\dagger})^{n_{\nu _2}} ... \ket{0} .
\end{multline}

As usual, by the appearance of the Minkowski metric in the non-zero commutator
\begin{equation} \label{eqn:ghosts}
	\Big[ \Hat{a}^{\mu} _{p} , (\Hat{a}^{\nu} _{k})^{\dagger} \Big] = \eta ^{\mu \nu} \delta _{p k} ,
\end{equation}
we have ghosts in the theory which must be dealt with. When translating the constraints as quantum operators, we require that they have vanishing matrix elements when sandwiched by physical states $\psi$ and $\phi$:
\begin{equation} \label{eqn:L-constraint-quantum-1}
	\bra{\phi} \Hat{L}_{p , k} \ket{\psi} = 0 \, \,
\end{equation}
\begin{equation} \label{eqn:L-constraint-quantum-2}
	\bra{\phi} \Hat{\widetilde{L}}_{p , k} \ket{\psi} = 0 .
\end{equation}
$\Hat{L}_{p , k}$ has no ambiguities since it's composed of only annihilation operators, however, we have an ambiguity for $\Hat{\widetilde{L}}_{p , 0}$. To resolve this issue, we pick
\begin{equation} \label{eqn:L-normal-ordering}
	\Hat{\widetilde{L}}_{p , 0} = \frac{- p}{E_{- p}} (\Hat{\alpha}^{\mu} _{p})^{\dagger} \Hat{\alpha}^{\nu} _{p} \eta _{\mu \nu}
\end{equation}
with the annihilation operator to the right, which manifests in the imposition of the constraint as
\begin{equation} \label{eqn:shifted-L-constraint}
	\bra{\phi} \Hat{\widetilde{L}}_{p , 0} - c_{p} \ket{\psi} = 0 ,
\end{equation}
for some sequence $c_{p}$. The reason for it to be a sequence of $p$ and not a constant like in the regular String Theory literature is that in the usual theory, we would have a sum over $p$ and thus it would end up being a constant, but in our analysis we have this extra freedom, which we'll now see ends up being important. Classically, we had eq(\ref{eqn:string-rest-mass}) for the string rest mass, which we can rewrite as
\begin{equation} \label{eqn:alternative-classical-rest-mass}
	M^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \lim _{n \rightarrow 0} \left( - \frac{E_{p}}{p} \widetilde{L}_{p , 0} \right) ,
\end{equation}
from where we can now see that the string mass spectrum will get shifted by
\begin{equation} \label{eqn:shifted-mass-spectrum}
	\Hat{M}^2 = - \frac{1}{(4 \pi (\alpha ')^2)^2} \left( (\Hat{\alpha} ^{\mu} _{0})^{\dagger} \Hat{\alpha}^{\nu} _{0} \eta _{\mu \nu} + \lim _{p \rightarrow 0} \frac{E_{p}}{p} c_{p} \right) .
\end{equation}
Since $E_{0} = \mu$, it seems like the natural candidate for $c_{p}$ would be some function $f (\mu , p)$ such that
\begin{equation} \label{eqn:cp-limit}
	\lim _{p \rightarrow 0} \frac{c_{p}}{p} = \mu
\end{equation}
like $c_{p} = \mu p$, $c_{p} = \sin (\mu p)$, $c_{p} = \tan (\mu p)$, etc, making it so the mass spectrum of the string gets shifted by the \textquotedblleft mass" term of the Klein-Gordon equation (\ref{eqn:X-Klein-Gordon-eqn}), $\mu ^2$.

The \textquotedblleft Virasoro-Klein-Gordon" algebra our constraint modes satisfy is given by
\begin{equation} \label{eqn:L-commutators-1}
	\Big[ \Hat{L}_{n , m} , \Hat{L}_{p , k} \Big] = 0
\end{equation}
\begin{multline} \label{eqn:L-commutators-2}
	\Big[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{m - n}{E_{m - n}} \Big( \Hat{L}_{n + k - p , n} \delta _{n - m , k} + \\
	+ \Hat{L}_{n - m + k - p , n - m} \delta _{n , k} \Big)
\end{multline}
\begin{multline} \label{eqn:L-commutators-3}
	\Big[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{(m - n)}{E_{m - n}} \frac{(k - p)}{E_{k - p}} \times \\
	\times \Bigg( \frac{E_{- n}}{(- n)} \Hat{\widetilde{L}}_{k - p - n , k - p} \delta _{n - m , k} + \\
	+ \frac{E_{- k}}{(- k)} \Hat{\widetilde{L}}_{n - m - k , n - m} \delta _{n , k - p} \Bigg) .
\end{multline}

@@

% \hline
